### 2018-12-18 README.Rmd
Add Hope & Schaefer 2016 Nature CC scenario data
Update README

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fortebaseline

@@

- `analysis/data/raw_data/schaefer_teb_rpc_(min/max/mean).csv` -- Raw, digitized versions of Figure 5c (Ensemble mean and uncertainty of permafrost C respiration) in [@schaefer_2011_amount]. Original figure is `analysis/data/raw_data/schaefer_teb_timeseries.gif`. These results were digitized using WebPlotDigitizer (https://apps.automeris.io/wpd/), and interpolated to annual resolution (using R `stats::spline` function).
    - [@schaefer_2011_amount] assume only CO2 emissions. So we add this as an extra anthropogenic CO2 flux.

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Hector permafrost emissions analysis

@@

- `analysis/data/raw_data/schaefer_teb_rpc_(min/max/mean).csv` -- Raw, digitized versions of Figure 5c (Ensemble mean and uncertainty of permafrost C respiration) in [@schaefer_2011_amount]. Original figure is `analysis/data/raw_data/schaefer_teb_timeseries.gif`. These results were digitized using WebPlotDigitizer (https://apps.automeris.io/wpd/), and interpolated to annual resolution (using R `stats::spline` function).
    - [@schaefer_2011_amount] assume only CO2 emissions. So we add this as an extra anthropogenic CO2 flux.
- `analysis/data/raw_data/hope_2016_Mt{CO2/CH4}_{lo/mean/hi}.csv` -- Raw, digitized versions of Figures 1 (permafrost CO2 emissions from SiBCASA) and 2 (same for CH4) from [@hope_2015_economic]. Same digitization and interpolation procedure. Original figures are `analysis/data/raw_data/hope_2016_nclimate_{co2,ch4}.jpg`.
